Demonstration of matching route networks

### 2024-02-13 r/demo.qmd
Update with more demos

x_segmented = stplanr::line_segment(x, segment_length = 10)
matches <- rnetmatch::rnet_match(x_segmented, y, dist_tolerance = 10, angle_tolerance = 5)
y_joined_segmented <- rnet_aggregate(x_segmented, y, matches, value)
sum(y_joined_segmented$value) # 
```

>>>>

x_segmented = stplanr::line_segment(x, segment_length = 10)
matches <- rnetmatch::rnet_match(x_segmented, y, dist_tolerance = 10, angle_tolerance = 5)
y_joined_segmented <- rnet_aggregate(x_segmented, y, matches, value)
y_joined_segmented
sum(y_joined_segmented$value)
```
